The resurgence of the linear optics interferometer --- recent advances \& applications

### 2017-05-10 paper.tex
Added to intro

\title{The Resurgence of the linear optics interferometer --- recent advances \& applications}

@@

In this review we will focus on single-photon encoding. Although other encodings, particularly those using continuous variable states of light exist, single-photon encodings seem to be the most promising. In the last decade, single photons have been produced mainly through spontaneous parametric down-conversion (SPDC), a nonlinear optical process. SPDC produces single photons in correlated pairs that has been the workhorse for providing entanglement in quantum states of light. Through much development in production schemes, and improvement in crystal quality, the number of high quality indistinguishable photons that can be concurrently produced have increased steadily over the years. Single-photon pairs are now run-of-the-mill business for quantum optical labs, and in the last five years, three photons are the landmark. The current record for single photons stand at ten. We have also seen the meteoric rise of quantum dots for this purpose. The latter has the advantage of on-demand single photon production, while SPDC is an inherently probabilistic process.

@@

A idealized single photon in a quantum interferometer is described by its creation operator $\adagh_{j}$, where $j$ is the label of the mode the photon is in  within the interferometer. The creation and annihilation operators satisfy the bosonic comutation relationship $[\ah_{j},\adagh_{k}]=\delta_{j,k}$. A similar commutation relationship can be written when additional degrees of freedom, such as polarization, orbital angular momentum, and time-bins \cite{bib:Tillmann2015,bib:Bozinovic2013, bib:Nicolas2014, bib:Humphreys2013, bib:Donohue2013}, are present. When multiple photons are present, they experience quantum interference when all quantum labels are the same.

>>>>

\title{The resurgence of the linear optics interferometer --- recent advances \& applications}

@@

In the last decade, single photons have been produced mainly through spontaneous parametric down-conversion (SPDC), a nonlinear optical process. SPDC produces single photons in correlated pairs that has been the workhorse for providing entanglement in quantum states of light. Through development and improvement in production schemes, the number of high quality indistinguishable photons that can be simultaneously produced have increased steadily over the years. Single-photon pairs, once a novelty, are now run-of-the-mill business for quantum optical labs, and in the last five years, three photons have become the standard benchmark. Experiments with up to ten photons have now been demonstrated. We have also seen the meteoric rise of quantum dots in the role for producing single photons. It is now possible to use a quantum dot to produce multiple single photons which are highly indistinguishable. Quantum dots produce single photons on demand, a significant advantage over SPDC which is an inherently probabilistic process.

The degree of control over single photons has also improved. Using advanced techniques and equipment to manipulate their polarization, time-of-arrival, and orbital angular momentum, new ways to engineer entangled quantum states and implement quantum operations have been discovered. These expand the toolbox of baseline resources we have for implementing quantum computations, which could prove crucial in the race to achieve quantum supremacy, that is, the demonstration of a computational task with a quantum  device that is not possible with any known algorithm running on an existing classical supercomputer in a reasonable amount of time,

In Section xxx, ...

@@

An idealized single photon in a quantum interferometer is described by its creation operator $\adagh_{j}$, where $j$ is the label of the mode the photon is in  within the interferometer. The creation and annihilation operators satisfy the bosonic comutation relationship $[\ah_{j},\adagh_{k}]=\delta_{j,k}$. A similar commutation relationship can be written when additional degrees of freedom, such as polarization, orbital angular momentum, and time-bins \cite{bib:Tillmann2015,bib:Bozinovic2013, bib:Nicolas2014, bib:Humphreys2013, bib:Donohue2013}, are present. When multiple photons are present, they experience quantum interference when all quantum labels are the same.
